# Figure 1: General overview of the data 
## STEP 1: Load packages
> Author: Ana Laura Hernández-Ledesma
> Contributions: Evelia Coss
> Date: Oct. 2025

```{r Load_libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggrepel) #prevents text to overlap
library(dplyr)
library(sf)
library(spData) #install.packages("spDataLarge",repos = "https://nowosad.github.io/drat/", type = "source")
library(ggmap)
library(reshape2)
library(mapdeck) #install.packages("mapdeck") ## to recover capitals coordinates
library(scatterpie) #install.packages("scatterpie") ## For scatterpie plots in the map
library(ggnewscale)
library(cowplot) # Join plots
```

```{r Set palettes}
# Set the color palette for ancestries, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
ancestry_pal  <- c(   "#b30000", "#f46d43", "#fee090", "#3f007d","#addd8e","#238443", "#80cdc1", "#de77ae")
names(ancestry_pal) <- c("AFR",     "As",      "EUR",     "ME",   "LA/NAd",  "NAm",      "O",     "Other")
scales::show_col(ancestry_pal) 

# Set the color palette for continents, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
continent_pal  <- c(     "#b30000", "#f46d43", "#fee090",  "#78c679",     "#80cdc1",   "#41ab5d")
names(continent_pal) <- c("Africa",   "Asia",  "Europe", "South America", "Oceania", "North America")
scales::show_col(continent_pal)

# Set the color palette for types of immune response, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
immune_response_pal  <- c(         "#92c5de","#f4a582","#fdb863","#b2abd2")
names(immune_response_pal) <- c("Innate response", "Adaptive response", "Antigen presentation", "Proinflammatory markers")
scales::show_col(immune_response_pal)

# Set the color palette for specific sub-ancestries, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
ancestries_palette  <- c(
   "#b30000", "#b2182b",
   "#d7301f","#f46d43","#f16913", "#fd8d3c", "#feb24c",
   "#fee090",
   "#3f007d","#54278f", "#54278f", "#6a51a3","#8073ac","#807dba","#8c96c6","#9e9ac8","#bcbddc", "#d8daeb","#efedf5",    
   "#addd8e",
   "#238443",
   "#80cdc1",
   "#de77ae",
   "#fee090","#f46d43", "#de77ae", "#b30000",   "#addd8e",   "#80cdc1",  "#3f007d",     "#41ab5d")

names(ancestries_palette) <- c(
  "AFR","AFR_Am",
  "SSA",  "As", "As_S", "As_SE", "EA",
  "EUR",
  "ME", "As,EUR", "As,O", "AFR,EUR,As,LA/NAd","AFR,EUR,LA/NAd", "AFR,LA/NAd", "AFR,LA/NAd,As,EUR", "EUR,AFR","EUR,LA/NAd,AFR", "EUR,LA/NAd,As,AFR","GME",
  "LA/NAd",
  "NAm",
  "O",
  "Other",
  "Europe", "Asia", "NR", "Africa", "Latin America","Oceania","Multicenter","North America" )
scales::show_col(ancestries_palette)

```
## STEP 2: Import data
```{r ImportData}
gwas_data <- read_tsv("~/Documents/R/Review/Immune_Response_db.tsv.gz")
head(gwas_data)
dim(gwas_data)

ancestries_p <- gwas_data %>%
  filter(general_ancestry=="NA")
```

## STEP 3: Figure 1a. Geographic distribution of the studies and frequency of reported  ancestries 
### Preparing the information regarding country of recruitment 
```{r recruitment}
recruitment <- gwas_data %>%
  # Select columns
   select(`COUNTRY OF RECRUITMENT`, `COUNTRY OF ORIGIN`, general_ancestry, recruitment_cont) %>%
  # Number of volunteers
  count(`COUNTRY OF RECRUITMENT`, `COUNTRY OF ORIGIN`, general_ancestry, recruitment_cont)

# Separate countries in columns
recruitment <- separate_wider_delim(recruitment, 
                       cols= `COUNTRY OF RECRUITMENT`,
                       delim = ",", 
                       names_sep = "", 
                       too_many = "debug",
                       too_few = "align_start")
# Select columns
recruitment <- recruitment %>%
  select( -`COUNTRY OF RECRUITMENTCOUNTRY OF RECRUITMENT`, -`COUNTRY OF RECRUITMENTCOUNTRY OF RECRUITMENTpieces`, -`COUNTRY OF RECRUITMENTCOUNTRY OF RECRUITMENTremainder`, -`COUNTRY OF RECRUITMENTCOUNTRY OF RECRUITMENTok` )

head(recruitment)[1:5]
```

### Selecting and plotting map for frequency and type of study
```{r world example}
data(world) ## in-build data set part of the spData package
plot(world["continent"], reset = FALSE)
```

### Extract countries from the database world
```{r Obtain Regions for mapping}
# -------- 1) Obtain Countries ---------------
regions <- data.frame(world$name_long, world$continent, world$subregion) ## mexico_departments 
regions$world.name_long <- as.factor(regions$world.name_long)
regions <-regions %>%
  rename(Country=world.name_long, Continent = world.continent, Subregion = world.subregion)

# Create an empty list to store the data
recruitment_list <- list()

# Create a loop for processing COUNTRY OF RECRUITMENT columns
for (i in 1:16) {
  recruitment_list[[i]] <- recruitment %>% 
    select(
      !!sym(paste0("COUNTRY OF RECRUITMENT", i)), 
      general_ancestry, 
      recruitment_cont
    ) %>% 
    rename(COUNTRY = !!sym(paste0("COUNTRY OF RECRUITMENT", i)))
}

# Merge all dataframes in the list into a single one
recruitment_all <- bind_rows(recruitment_list)

# -------- 2) Prepare data for the plot ---------------
# Create a replacement vector with the necessary corrections for country names
country_replacements <- c(
  "Iran (Islamic Republic of)" = "Iran",
  "U.K." = "United Kingdom", 
  " U.K." = "United Kingdom", 
  "U.S." = "United States", 
  " U.S." = "United States", 
  " Hong Kong SAR"="Hong Kong SAR",
  " Canada" = "Canada",
  " Belgium" = "Belgium",
  " China" = "China",  
  " Croatia" = "Croatia",
  " Denmark" = "Denmark",
  " Estonia" = "Estonia",
  " Finland" = "Finland",
  " France" = "France",
  " Germany" = "Germany",
  " Greece" = "Greece",
  " Italy" = "Italy",
  " Japan" = "Japan",
  " Netherlands" = "Netherlands",
  " Uganda" = "Uganda",
  " Iceland" = "Iceland",
  " Poland" = "Poland",
  " NR" = "NR",
  " Republic of Korea" = "Republic of Korea",
  " Singapore" = "Singapore",
  " Sweden" = "Sweden",
  " Taiwan" = "Taiwan",
  " Australia" = "Australia",
  " Austria" = "Austria",
  " Brazil" = "Brazil",
  " Costa Rica" = "Costa Rica",
  " Czech Republic" = "Czech Republic",
  " Hungary" = "Hungary",
  " Kenya" = "Kenya",
  " Lithuania" = "Lithuania",
  " New Zealand" = "New Zealand",
  " Niger" = "Niger",
  " Nigeria" = "Nigeria",
  " Norway" = "Norway",
  " Peru" = "Peru",
  " Republic of Ireland" = "Ireland",
  " Slovenia" = "Slovenia",
  " South Africa" = "South Africa",
  " Spain" = "Spain",
  " Switzerland" = "Switzerland",
  " Turkey" = "Turkey"
)

# Apply substitutions using dplyr
data <- recruitment_all %>%
  na.omit() %>%
  rename(Country = COUNTRY) %>%
  mutate(Country = recode(Country, !!!country_replacements)) %>%
  count(Country)

recruitment_all <- recruitment_all %>%
  na.omit() %>%
  rename(Country = COUNTRY) %>%
  mutate(Country = recode(Country, !!!country_replacements))

# Results
data
```
### Join the databases
```{r plot construction}
# -------- 3) Join databases by country and plot ---------------

#Preview map plot
regions <- regions %>%
  dplyr::left_join(y=data, by = "Country")

# Convert foreign object to an sf object
sf_data <- st_as_sf(world) ## aquí van las coordenadas
sf_data <- sf_data %>% 
  rename(Country = name_long)
# View(sf_data)

sf_data_studies <- sf_data %>% #data for graphic
  left_join(y = regions, by = "Country")
# View(sf_data_studies)

##Plotting
worldmap <- sf_data_studies %>% 
  ggplot(mapping = aes(fill = n)) +
  geom_sf() +
  scale_fill_gradientn(colours=c("#67a9cf", "#f46d43"),
                         na.value = "grey100",
                       limits = c(1, 60))+ # Adjust the limit values
  labs(title = "Immunogenetics studies in underrepresented populations",
       fill = "Number of studies") + 
  theme_void() + # eliminate axes
  theme(plot.title = element_text(hjust = 0.5))


### Scatterpie for ancestries contribution
##Select data
data_sp <- recruitment_all 

## Counting frequencies
data_sp <- data_sp %>%
  count(Country, general_ancestry) %>%
  rename(Freq= n) ##mexico_b

## Estimate frequencies by country
sp_ancestry <- dcast(data_sp, Country ~ general_ancestry, value.var = "Freq")

sf_ancestry <- sf_data_studies %>% #data for graphic
  left_join(y = sp_ancestry, by = "Country")
# View(sf_ancestry)

## Add coordinates
capitals_coordinates <- capitals %>% 
  rename(Country =country)

#write_csv(capitals_coordinates, "~/Documents/R/Review/capitals.csv")
capitals_coordinates <-  read_csv("~/Documents/R/Review/capitals.csv")

capitals_coordinates <- capitals_coordinates %>%
  left_join(y= sf_ancestry, by ="Country")

# View(capitals_coordinates)

##Setting na's as 0 before plotting
ancestry_capital <- capitals_coordinates %>%
  select(Country, lat, lon, Continent, n, "AFR","As","EUR","ME", "LA/NAd","NAm","O","Other" ) %>%
  mutate(across(where(is.numeric), ~replace_na(. , 0)))  # Change NAs to 0 in numeric columns

## Plotting map and scatterpie 
# Scatter plots
#Preview scatterpies with ancestries proportions
ggplot()+
  geom_scatterpie(aes(x=lon, y=lat), 
                  data=ancestry_capital, 
                  cols= c("AFR","As","EUR","ME", "LA/NAd", "NAm","O","Other"))+
  scale_fill_manual(values = ancestry_pal)+
  theme_minimal()+
  theme(legend.position = 'bottom')

##Bind map and scatterpies
ggplot() +
  geom_scatterpie(aes(x=lon, y=lat), 
                  data=ancestry_capital, 
                  cols= c("AFR","As","EUR","ME", "LA/NAd","NAm","O","Other"),
                  pie_scale = 0.9,
                  legend_name = "Ancestry",
                  linewidth=0.2)+
  scale_fill_manual(values = ancestry_pal)+
  theme_minimal()+
  theme(legend.key.size = unit(0.3,'cm'),
        legend.position = 'bottom',
        legend.title = element_text(size=8),
        legend.text = element_text(size=8))+
    labs(title = "Immunogenetics studies in underrepresented populations",
       fill = "Number of studies") + 
  theme(plot.title = element_text(hjust = 0.5))

sf_data_studies$n[is.na(sf_data_studies$n)] <- 0 ##changing NAs to 0
sf_data_studies$n <- as.numeric(sf_data_studies$n)
# class(sf_data_studies$n) # numeric

#Plotting number of studies, ancestries and geographic distribution
fig1a <- ggplot() +
  geom_sf(data= sf_data_studies, aes(fill = n)) +
  scale_fill_gradientn(colours=c("#e1ecff","#bf812d"),
                         na.value = "grey100",
                       limits = c(1, 50))+ # Adjust the limit values
  new_scale_fill()+ ## to assign a new color scale 
  geom_scatterpie(aes(x=lon, y=lat),
                  data=ancestry_capital, 
                  cols= c("AFR","As","EUR","ME","LA/NAd","NAm","O","Other"),
                   pie_scale = 0.5,
                  linewidth=0.2,
                  alpha=0.7)+
  scale_fill_manual(values = ancestry_pal)+
  theme_minimal()+
  theme(legend.key.size = unit(0.2,'cm'),
        legend.position = "inside",
        legend.position.inside = c(0.10,0.45),
        legend.title = element_text(size=8, hjust = 0.5, face = "bold"),
        legend.text = element_text(size=8),
        theme(plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        plot.title = element_text(hjust = 0.9)))+
  labs(title = "A. Geographic distribution of studies",
       fill = "Ancestry")
fig1a

# Save plot
ggsave(filename= "Figures/Figure_1_map.png", plot= fig1a, width = 11, height = 8, dpi=300, units = "in", bg = "white" )

recruitment_df <- sf_data_studies %>%
  select(Continent, Country, n) 

total_countries <- sum(recruitment_df$n)
total_countries

recruitment_countries <- sf_data_studies %>%
  select(Country, n) %>%
  mutate(percent = n / sum(total_countries) * 100)

recruitment_europe <- sf_data_studies %>%
  select(Continent, Country, n)  %>%
  filter(Continent == "Europe")

recruitment_europe <- recruitment_europe  %>%
  mutate(percent = n / sum(total_countries) * 100)  

recruitment_perc <- recruitment_df%>%
  group_by(Continent) %>%
  summarise(total_n = sum(n, na.rm = TRUE))%>%
  ungroup() %>%
  mutate(percent = total_n / sum(total_n) * 100)


```

## STEP 4: Figure 1b. Analysis of reported ancestries by geographic region of recruitmen
```{r Descriptive analysis of the recruitment and ancestries}
# Select data
studies_desc <- sf_data_studies %>%
  select(Country, Continent,n) %>%
  filter(n>=1)
sum(sf_data_studies$n) #370

##Count by continent of recruitment
studies_continent <- sf_data_studies %>%
  group_by(Continent) %>%
  summarise(suma = sum(n, na.rm=TRUE),
            .groups="drop")
continent_sum<- sum(studies_continent$suma)

## Calculate percentages
studies_continent <- studies_continent %>% 
 mutate(percentage = round(((suma*100)/continent_sum)))

##Count by country of recruitment
studies_country <- sf_data_studies %>%
  group_by(Country) %>%
  summarise(suma = sum(n, na.rm=TRUE),
            .groups="drop")

country_sum<- sum(studies_country$suma)

## Calculate percentages
studies_country <- studies_country%>% 
 mutate(percentage = round(((suma*100)/country_sum)))

### ancestries by continent and 
ancestry_capital <- ancestry_capital%>% 
    mutate(
    Continent = case_when(
      Country == "Mexico" ~ "Latin America",  ## To consider Mexico as Latin America rather than North America  
      Country == "Costa Rica" ~ "Latin America", ## To consider CR as Latin America rather than North America
      Continent == "South America" ~ "Latin America",
      TRUE ~ Continent
    )
  )
studies_ancestries <- ancestry_capital%>% 
  select(Continent, n, AFR, As, EUR, ME, "LA/NAd", "NAm", O, Other)%>%
  filter(n>=1) # To keep only studies with reported ancestries

total_ancs <- sum(studies_ancestries$n)

total_ancestries <- studies_ancestries %>%
  select(-Continent, -n)
 
ancs_sum <- colSums(total_ancestries, na.rm = TRUE)

# Convert into tibble 
ancs_sum_df <- as_tibble(as.list(ancs_sum))

anc_perc_df <- ancs_sum_df %>%
    rename(LA_NAd = `LA/NAd`,NA_col = `NAm`) %>%
  mutate(
    AFR_pct=AFR / total_ancs * 100,
    As_pct=As  / total_ancs * 100,
    EUR_pct=EUR / total_ancs * 100,
    ME_pct=ME / total_ancs * 100,
    LA_NAd_pct= LA_NAd/ total_ancs * 100,
    NA_pct= NA_col/ total_ancs * 100,
    O_pct=O/total_ancs * 100
  )

##Count of ancestry by continent of recruitment
studies2 <- studies_ancestries %>%
  rename(
    LA_NAd = `LA/NAd`, 
    NA_col = `NAm`
  )

ancestries_continent <- studies2 %>%
  group_by(Continent) %>%
  summarise(
    across(c(AFR, As, EUR, ME, LA_NAd, NA_col),
           ~ sum(.x, na.rm = TRUE),
           .names = "{.col}_sum"),
    .groups = "drop"
  ) %>%
  mutate(
    total = rowSums(across(ends_with("_sum"))),
    # calcular porcentaje solo si total > 0
    AFR_pct   = if_else(total > 0, AFR_sum / total * 100, NA_real_),
    As_pct    = if_else(total > 0, As_sum / total * 100, NA_real_),
    EUR_pct   = if_else(total > 0, EUR_sum / total * 100, NA_real_),
    ME_pct    = if_else(total > 0, ME_sum / total * 100, NA_real_),
    LA_NAd_pct= if_else(total > 0, LA_NAd_sum / total * 100, NA_real_),
    NA_pct    = if_else(total > 0, NA_col_sum / total * 100, NA_real_)
  )

# Pivot to long, group and calculate percentages
percentages_by_continent <- studies2 %>%
  pivot_longer(
    cols = c(AFR, EUR, As, ME, LA_NAd, NA_col),
    names_to = "Ancestry",
    values_to = "Count"
  ) %>%
  group_by(Continent, Ancestry) %>%
  summarise(
    sum_count = sum(Count, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(Ancestry) %>%
  mutate(
    total = sum(sum_count),
    pct = if_else(total > 0, sum_count / total * 100, NA_real_)
  ) %>%
  ungroup()

```

## Create plot
```{r Plot ancestries by geographic region}
# Select data
gwas_desc <- gwas_data %>% 
  select(DATE, PUBMEDID, `DISEASE/TRAIT`, `BROAD ANCESTRAL CATEGORY`, `COUNTRY OF ORIGIN`, `COUNTRY OF RECRUITMENT`, SNPS, sp_ancestry, recruitment_cont, response, Global_response, sp_ancestry, general_ancestry)

# Recover year of the GWAS
gwas_desc$date <- as.Date(gwas_desc$DATE, format = "%Y/%m/%d")
gwas_desc$year <- format(gwas_desc$date, "%Y")

gwas_rec <- gwas_desc %>% 
  select(year, PUBMEDID, recruitment_cont, general_ancestry, `BROAD ANCESTRAL CATEGORY`)%>% 
  unique()

gwas_rec_studies <- gwas_rec %>% 
  mutate(group = (if_else(`BROAD ANCESTRAL CATEGORY` == "European", "European", "Non-European")))

gwas_rec_studies <- gwas_rec_studies %>%
  mutate(
    year = as.numeric(year), 
    group = factor(group))

gwas_rec_studies <- gwas_rec_studies %>% 
  count(group, general_ancestry, recruitment_cont,year )

# Create variable to separate columns
gwas_rec_2 <- gwas_rec_studies  %>%
  mutate(x_pos = ifelse(group == "European", as.numeric(factor(year)) - 0.15,
                        as.numeric(factor(year)) + 0.15))
cont_groups <- gwas_rec_2  %>%
  select(recruitment_cont) %>%
  group_by(recruitment_cont) %>%
  count()

gwas_rec_2 <- gwas_rec_2  %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "Europe-Asia", "Multicenter")) %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "Europe-Asia-North America", "Multicenter")) %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "Europe-North America", "Multicenter")) %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "Europe-Oceania", "Multicenter")) %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "Europe-Oceania-North America", "Multicenter")) %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "North America-Latin America-Europe", "Multicenter")) %>%
  mutate(recruitment_cont = replace(recruitment_cont, recruitment_cont == "Russian Federation", "Multicenter"))%>%
  filter(recruitment_cont != "No reported")

studies_ancestries_pct<- ancestries_continent %>%
  select(Continent, "AFR_pct","As_pct","EUR_pct","ME_pct","LA_NAd_pct","NA_pct" )%>%
  mutate(Continent = replace(Continent, Continent == "North America", "North\n America"))%>%
  mutate(Continent = replace(Continent, Continent == "Latin America", "Latin\n America"))

df_long <- studies_ancestries_pct %>%
  pivot_longer(cols = ends_with("pct"), 
               names_to = "Ancestry", 
               values_to = "Percentage")

df_long <- df_long %>%
   mutate(Ancestry = replace(Ancestry, Ancestry== "AFR_pct", "AFR"))%>%
   mutate(Ancestry = replace(Ancestry, Ancestry== "As_pct", "As"))%>%
   mutate(Ancestry = replace(Ancestry, Ancestry== "EUR_pct", "EUR"))%>%
   mutate(Ancestry = replace(Ancestry, Ancestry== "ME_pct", "ME"))%>%
   mutate(Ancestry = replace(Ancestry, Ancestry== "LA_NAd_pct", "LA/NAd"))%>%
   mutate(Ancestry = replace(Ancestry, Ancestry== "NA_pct", "NAm"))

## Plot proportion of ancestries reported by geographic region
fig1b <-ggplot(df_long, aes(x = Continent, y = Percentage, fill = Ancestry)) +
  geom_bar(stat = "identity") +
  labs(title = "Ancestries distribution by region of recruitment",
       x = "Geographic region",
       y = "Percentage (%)") +
  theme_minimal() + 
  scale_fill_manual(values = ancestries_palette) +
  labs(title = "B. Ancestries per region of recruitment",
       x = "Region of recruitment", y = "Studies (%)",
       fill = "Ancestries") +
  theme(legend.position = "right",
        legend.key.size = unit(0.5,'cm'),
        plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 10),
        axis.title.x = element_text(size = 10, face = "bold"), 
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 10, face = "bold"))
fig1b
```

## STEP 5: Figure 1c. Analysis through time of studies associated with European and non-European ancestries
```{r Time analysis of reported ancestries in the included studies}
# Select data
# Keep only unique GWAS
gwas_anc <- gwas_desc %>% 
  select(year, PUBMEDID, `BROAD ANCESTRAL CATEGORY`, recruitment_cont,sp_ancestry, general_ancestry)%>% 
  unique()

gwas_anc_studies <- gwas_anc %>% 
  select(PUBMEDID)%>% 
  unique()

# Group in European vs non-European
gwas_anc <- gwas_anc %>% 
  mutate(group = (if_else(`BROAD ANCESTRAL CATEGORY` == "European", "European", "Non-European")))

gwas_anc <- gwas_anc %>%
  mutate(
    year = as.numeric(year), 
    group = factor(group))

gwas_anc_2 <- gwas_anc %>% 
  count(year, group, general_ancestry)

# Variable to separate bars
gwas_anc_3 <- gwas_anc_2 %>%
  mutate(x_pos = ifelse(group == "European", as.numeric(factor(year)) - 0.15,
                        as.numeric(factor(year)) + 0.15))

# Plot Studies by ancestry by year
fig1c <- ggplot() +
  # Europeans (simple bar)
  geom_col(data = gwas_anc_3 %>% filter(group == "European"),
           aes(x = x_pos, y = n),
           colour = "#bdbdbd",
           fill = "#fee090",
           alpha = 0.6,
           width = 0.4) +
  # Non-Europeans (stacked bar)
  geom_col(data = gwas_anc_3 %>% filter(group == "Non-European"),
           aes(x = x_pos, y = n, fill = general_ancestry),
           alpha = 0.8,
           width = 0.4) +
  scale_fill_manual(values = ancestries_palette) +
  scale_x_continuous(breaks = 1:length(unique(gwas_anc_3$year)),
                     labels = unique(gwas_anc_3$year)) +
  labs(title = "C. Studies per year: Europeans vs Non-Europeans",
       x = "Year", y = "Number of studies",
       fill = "Sub-ancestries (Non-Europeans)") +
  theme_minimal()+
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5),
        axis.text.x = element_text(size = 10, angle = 90),
        axis.title = element_text(size = 10, face = "bold"), 
        axis.text.y = element_text(size = 8, , face = "bold"))
fig1c

# Join plots b and c
fig1bc <- plot_grid(  
  fig1b,fig1c, 
  labels = c("",""),
  ncol=2,
  rel_widths = c(1.2, 1),
  panel_spacing= unit(0.5, "cm"),
  label_size = 20, 
  label_fontface = "bold",
  label_colour = "black")
fig1bc

# Save plot
ggsave(filename= "Figures/Figure_1bc.png", plot= fig1bc, width = 10, height = 5, dpi=300, units = "in", bg = "white" )

# Join final figure 
fig1 <- plot_grid(  
  fig1a, fig1bc,
  labels = c("",""),
  ncol=1,
  rel_heights = c(1.7, 2),
  panel_spacing= unit(0.2, "cm"))
fig1

# Save plot
ggsave(filename= "Figures/Figures_PDF/Figure_1.pdf", plot= fig1, width = 10, height = 15, dpi=300, units = "in", bg = "white" )
ggsave(filename= "Figures/Figure_1.png", plot= fig1, width = 10, height = 15, dpi=300, units = "in", bg = "white" )

```



