# Figure 3: SNPs distribution within non-european populations
> Author: Ana Laura Hernández-Ledesma
> Contributions: Evelia Coss
> Data: Oct 2025

## STEP 1: Load Global information
Load packages

```{r, message=FALSE, warning=FALSE}
library(RColorBrewer)
library(tidyverse)
library(cowplot) # Join plots
library(circlize)
library(ggpubr) # ggplot2 extension to create quick and customizable plots
library(ggforce) # ggplot2 extension to create complex plots
library(ggrepel) # prevent texts to overlap
library(extrafont) # fonts
library(ggtext)
library(ComplexHeatmap) # heatmaps y upsetR 
library(gridGraphics) # Join heatmaps 
library(grid)  # Heatmap adjustment
library(magick)
library(patchwork)
library(gridExtra)
library(png)
library(DT) #table
```

Load colorblind palette

```{r SetPalette}
# Set the color palette for ancestries, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
ancestry_pal  <- c(   "#b30000", "#f46d43", "#fee090", "#3f007d","#addd8e","#238443", "#80cdc1", "#de77ae")
names(ancestry_pal) <- c("AFR",     "As",      "EUR",     "ME",   "LA/NAd",  "NA",      "O",     "Other")
scales::show_col(ancestry_pal) 

# Set the color palette for continents, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
continent_pal  <- c(     "#b30000", "#f46d43", "#fee090",  "#78c679",     "#80cdc1",   "#41ab5d")
names(continent_pal) <- c("Africa",   "Asia",  "Europe", "South America", "Oceania", "North America")
scales::show_col(continent_pal)

# Set the color palette for types of immune response, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
immune_response_pal  <- c(         "#92c5de",           "#f4a582",            "#a6dba0",                 "#b2abd2")
names(immune_response_pal) <- c("Innate response", "Adaptive response", "Antigen presentation", "Proinflammatory markers")
scales::show_col(immune_response_pal)

# Set the color palette for specific sub-ancestries, using https://colorbrewer2.org/#type=diverging&scheme=BrBG&n=9 colorblind options
ancestries_palette  <- c(
   "#b30000", "#b2182b",
   "#d7301f","#f46d43","#f16913", "#fd8d3c", "#feb24c",
   "#fee090","#166866",
   "#3f007d","#54278f", "#54278f", "#6a51a3","#8073ac","#807dba","#8c96c6","#9e9ac8","#bcbddc", "#d8daeb","#efedf5",    
   "#addd8e",
   "#238443",
   "#80cdc1",
   "#de77ae",
   "#fee090","#f46d43", "#de77ae", "#b30000",   "#addd8e",   "#80cdc1",  "#3f007d",     "#41ab5d")

names(ancestries_palette) <- c(
  "AFR","AFR_Am",
  "SSA",  "As", "As_S", "As_SE", "EA",
  "EUR","nonE",
  "ME", "As,EUR", "As,O", "AFR,EUR,As,LA/NAd","AFR,EUR,LA/NAd", "AFR,LA/NAd", "AFR,LA/NAd,As,EUR", "EUR,AFR","EUR,LA/NAd,AFR", "EUR,LA/NAd,As,AFR","GME",
  "LA/NAd",
  "NA",
  "Oceanian",
  "Other",
  "Europe", "Asia", "NR", "Africa", "Latin America","Oceania","Multicenter","North America" )
scales::show_col(ancestries_palette) 

# funtional / Variant association
var_association_pal  <- c(     "#6E46AF", "#A5EBB3", "#FFD987", "#A1183E",   "#FC924B",  "#E1AE01")
names(var_association_pal) <- c("Coding", "Promoter", "UTR",   "Accesible", "Intronic", "Intergenic")
scales::show_col(var_association_pal)

# Variants consequences
var_association_pal <- c("#D9D9D9","#B2DF8A","#FB9A99","#FDBF6F","#F0E442","#C8B8DB","#66C2A5", "#FC8D62","#8DA0CB", 
                         "#E78AC3","#A6D854","#FFD92F","#E41A1C","#BDBDBD")
names(var_association_pal) <- c(
  "Intergenic","Intron","UTR","Missense variant","Regulatory region","Inframe insertion", "Synonymous", "Splice region variant", "TF binding site","Splice polypyrimidine tract variant", "Splice donor 5th base variant","Splice donor variant","Stop gained","No reported")
scales::show_col(var_association_pal)

# Impact of variants
impact_pal <- c(     "#D73027", "#FC8D59","#FEE08B", "#D9EF8B",  "#BDBDBD")
names(impact_pal) <- c("High" ,"Moderate", "Low",   "Modifier","No reported")
scales::show_col(impact_pal)
```
## STEP 2: Order of file rows and columns
```{r}
# Define the desired order for Global_response
orden_global_response <- c("Adaptive response", "Antigen presentation", "Proinflammatory markers", "Innate response", "No reported")

# Possible types of immune response
immune_types <- c("Innate response", "Adaptive response", "Antigen presentation", "Proinflammatory markers", "No reported")

# Order of answers
orden_response <- c(
      # Adaptive
      "Antibodies", "T cells", "B cells",
      # Antigen presentation
      "DCs", "HLA",
      # Proinflammatory markers
      "IL-1", "IL-6", "IL-12", "IL-18", "CRP", "TNF", "IFN", "Chemiokines",
      # Innate response
       "Neutrophil", "Monocyte", "Basophil",   "Physical Barriers", "Eosinophil", "NK",  
       "Coagulation cascade", "Inflammatory mediators", "Complement", "Macrophage", "Adhesion molecules",  "Pattern recognition",  "Mast cells", "Leukocytes",  "Growth factors")
```


Global variable with immune response in SNPs and ancestries.

```{r GlobalData, warning=FALSE, message=FALSE}
gwas_data <- read_tsv("data/Immune_Response_db.tsv.gz")

# Check
unique(gwas_data$Global_response)
```

## STEP 3: Data preparation: exploration of non-european ancestries data
Shared SNPs between ancestries.

```{r}
# Select data
gwas_data_ancestries <- gwas_data %>%
  select(general_ancestry, Global_response, response, CHR_ID, SNPS, 
         StudyID, CONTEXT, `FIRST AUTHOR`, `DATE`, `INITIAL SAMPLE SIZE`, PUBMEDID, MAPPED_GENE) %>%
  # unique SNPs 
   distinct()

table(gwas_data_ancestries$general_ancestry)
```
### Table about papers (with EUR)
Number of papers related to immune response.

```{r}
unique(gwas_data_ancestries$StudyID) %>% length()
```

### About SNPs data
Shared SNPs between ancestries. Count how many and which ancestries are associated with each SNP.
```{r}
# Number of Shared SNPs
snps_by_ancestry <- gwas_data_ancestries %>%
  group_by(SNPS) %>%
  summarise(n_ancestries = n_distinct(general_ancestry),
            ancestries = paste(unique(general_ancestry), collapse = ", ")) %>%
  arrange(desc(n_ancestries))
head(snps_by_ancestry)
```

Non-European population SNPs.
```{r}
# Table with all ancestries
EUR_SNPS_db <- snps_by_ancestry %>%
  filter(ancestries == "EUR")  # ancestria Europea

NonEUR_SNPS_db <- snps_by_ancestry %>%
  group_by(ancestries) %>%
  mutate(Group = ifelse(str_detect(ancestries, "\\bEUR\\b") & !str_detect(ancestries, "!EUR"), 
                        "EUR-related SNPs", 
                        "Non-EUR-related SNPs")) %>%
  filter(Group == "Non-EUR-related SNPs") # sin ancestria Europea

NonEUR_SNPS_db2 <- NonEUR_SNPS_db %>%
  group_by(ancestries) %>%
  mutate(Group = ifelse(str_detect(ancestries, "\\bME\\b") & !str_detect(ancestries, "!ME"), 
                        "EUR-related SNPs", 
                        "Non-EUR-related SNPs")) %>%
  filter(Group == "Non-EUR-related SNPs") # sin ancestria Europea

# Check for the SNPs that are not present in Europeans
NonEUR_SNPs_filter <- anti_join(NonEUR_SNPS_db2, EUR_SNPS_db, by = "SNPS")

```

Data without European SNPs.
```{r}
# Select data from non-European ancestries
gwas_data_cleaned <- gwas_data_ancestries %>%
  # select specific columns, according with the analysis
  select(Global_response, general_ancestry, response, CHR_ID, SNPS, 
         StudyID, CONTEXT) %>%
  # SNPs that are not shared with European ancestries
  filter(SNPS %in% NonEUR_snps) %>% 
  filter(general_ancestry != "ME") %>% 
  # Keep only unique SNPs 
  distinct(SNPS, .keep_all = TRUE)  
  
dim(gwas_data_cleaned)  
```
1,875 unique, non-redundant SNPs, some of which are repeated or shared between ancestries.

### Table 1: About papers (without EUR)

Large GWAS sample size by global response and ancestry for single and multi-ancestry studies.
```{r}
Table1_papers_MEancestry <- gwas_data_ancestries %>%
  # Clean data related with Study ID (without EUR)
  filter(StudyID %in% unique(gwas_data_cleaned$StudyID)) %>%
  # Order and select columns
  select(Global_response, response, general_ancestry, `FIRST AUTHOR`, `DATE`, `INITIAL SAMPLE SIZE`, PUBMEDID) %>%
  # Single paper per row
  distinct(PUBMEDID, .keep_all = TRUE) %>%
  # rename columns
  rename("Immune response" = Global_response, Response = response, Ancestry  = general_ancestry,
    Year = DATE, "Firt Author" = `FIRST AUTHOR`, "Total samples" = `INITIAL SAMPLE SIZE`, "PUDMED ID" = PUBMEDID)

# Obtain only year
Table1_papers_MEancestry$Year <- format(as.Date(Table1_papers_MEancestry$Year), "%Y")
  
# Show information
Table1_papers_MEancestry %>%
  DT::datatable()
```

## STEP 4: Clean data acoording with Non-EUR SNPs (list)
```{r snps_by_ancestry_list}
# Data set para Upset R
# Create list of SNPs by ancestry
snps_by_ancestry_list <- gwas_data_ancestries %>% 
  filter(SNPS %in% NonEUR_snps) %>% # SNPs from non-European populations
  group_by(general_ancestry) %>%
  filter(general_ancestry != "ME") %>%
  summarise(SNPs = list(unique(SNPS)), .groups = "drop") %>%
  deframe()  # Converts the dataframe to a list

```

## STEP 5:  Figure 3a. Ancestry-specific variants
```{r Proportion of Ancestry-specific variants}
# Prepare data
immune_snps <- gwas_data_ancestries %>%
  group_by(general_ancestry) %>%
  mutate(Group = ifelse(str_detect(general_ancestry, "\\bEUR\\b") & !str_detect(general_ancestry, "!EUR"), 
                        "EUR-related SNPs", 
                        "Non-EUR-related SNPs")) %>%
filter(Group == "Non-EUR-related SNPs")
  
immune_snps_1 <- immune_snps %>%
  group_by(general_ancestry) %>%
  mutate(Group = ifelse(str_detect(general_ancestry, "\\bME\\b") & !str_detect(general_ancestry, "!ME"), 
                        "EUR-related SNPs", 
                        "Non-EUR-related SNPs")) %>%
  filter(Group == "Non-EUR-related SNPs") 

immune_snps_2 <- immune_snps_1 %>%
  group_by(general_ancestry) %>%
  mutate(Group = ifelse(str_detect(general_ancestry, "\\bOther\\b") & !str_detect(general_ancestry, "!ME"), 
                        "EUR-related SNPs", 
                        "Non-EUR-related SNPs")) %>%
  filter(Group == "Non-EUR-related SNPs") 

# Identify ancestries by SNP
snp_ancestry <- immune_snps_2 %>%
  group_by(SNPS) %>%
  summarise(n_ancestries = n_distinct(general_ancestry), .groups = "drop")

# Classify SNPs in the original dataframe
snp_ancestry_group <- immune_snps_2%>%
  left_join(snp_ancestry, by = "SNPS") %>%
  mutate(Category = ifelse(n_ancestries == 1, "Unique", "Shared"))

# Count shared and exclusive SNPs
ancestries_sum <- snp_ancestry_group %>%
  group_by(general_ancestry, Category) %>%
  summarise(Count = n_distinct(SNPS), .groups = "drop") %>%
  group_by(general_ancestry) %>%
  mutate(Proportion = Count / sum(Count) * 100)

# Set color palette
colors <- c("Unique" = "#1f78b4", 
            "Shared" = "#a6cee3")  

# Plot
fig3a <- ggplot(ancestries_sum, aes(x = general_ancestry, y = Proportion, fill = Category)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = colors) +
  labs(title = "A. Proportion of ancestry-specific and shared variants",
       x = "Ancestry",
       y = "Proportion of SNPs (%)",
       fill = "SNP Type") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5,  face = "bold"),
    legend.key.size = unit(0.3,'cm'),
    axis.text.x = element_text(size = 8, hjust = 0.5),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size=8),
    axis.title = element_text(size = 8, face = "bold"), 
    axis.text.y = element_text(size = 8))
fig3a 
```

## STEP 6:  Figure 3b. Immune traits associated with ancestry-specific variants
```{r Immune traits associated with ancestry-specific variants}
# Check for the SNPs that are ancestry-specific
immune_snps_3 <- immune_snps_2 %>%
  select(general_ancestry, Global_response, SNPS)

immune_snps_exclusive <- immune_snps_3 %>%
  group_by(SNPS) %>%
  mutate(n_ancestries = n_distinct(general_ancestry)) %>%  # count how many ancestries does a SNP have
  filter(n_ancestries == 1) %>%                            # Keeping the ancestry-exclusive SNPs
  ungroup()

immune_snps_4 <-immune_snps_exclusive %>%
  count(general_ancestry, Global_response, name = "exclusive_SNPs") 

fig3b <- ggplot(immune_snps_4 , aes(x = general_ancestry, y = Global_response, size = exclusive_SNPs, color = Global_response)) +
  geom_point(alpha = 0.7) +
  scale_size(range = c(2, 10)) +  # Bubble size
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold"),
    legend.key.size = unit(0.1,'cm'),
    axis.text.x = element_text(size = 8, hjust = 0.5),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size=8),
    axis.title = element_text(size = 8, face = "bold"), 
    axis.text.y = element_text(size = 8),
    legend.box = "vertical"
  ) +
  labs(
    title = "B. Frequency of immune-associated traits \namong ancestry-specific variants",
    x = "Ancestry",
    y = "Immune Response",
    size = "Number of SNPs",
    color = "Immune Response"
  )+
  guides(
    color = "none",
    size = guide_legend(override.aes = list(size = 3)))

#Join plots
fig_3ab <- plot_grid(
  fig3a, fig3b,
  labels = c("", ""),
  ncol = 2
)
fig_3ab

```

## STEP 7:  Figure 3c. Distribution of unique ancestry-specific variants
```{r Distribution of unique ancestry-specific variants}
### Check for the SNPs that are ancestry-specific
## Select only exclusive snps
excl_snps <- immune_snps_2 %>%
  select(general_ancestry, Global_response,response, CHR_ID, SNPS)


excl_snps2 <- excl_snps %>%
  group_by(SNPS) %>%
  mutate(n_ancestries = n_distinct(general_ancestry)) %>% 
  filter(n_ancestries == 1) %>% # Keeping the ancestry-exclusive SNPs
  ungroup()

#Summarise
snps_sum <-excl_snps2 %>%
  group_by(CHR_ID, Global_response, general_ancestry) %>%
  summarise(n_snp = n_distinct(SNPS), .groups = "drop") %>%
  filter(!is.na(CHR_ID))

# Set chromosome order
orden_CHR_ID <- c(as.character(1:22), "X", "Y")
snps_sum$CHR_ID <- factor(snps_sum$CHR_ID, levels = orden_CHR_ID)
snps_sum <-snps_sum %>%
  filter(!is.na(CHR_ID))

fig3c<-  ggplot(snps_sum, aes(x = CHR_ID, y = n_snp, fill = Global_response)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = immune_response_pal)+ 
  facet_wrap(~ general_ancestry, scales = "free_y", ncol = 1) +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold"),
    panel.grid.major.x = element_blank(),
    legend.position = "none",
    legend.title = element_blank(),
    axis.title.x = element_text(size = 8, face = "bold"),
    axis.title.y = element_text(size = 8, face = "bold"),
    axis.text.x = element_text(size =8)) +
  labs(title = "C. Genomic distribution of unique ancestry-specific variants by ancestry",
     x = "Chromosome", y = "Unique SNPs")
fig3c
```

## STEP 8:  Figure 3d. Enrichment of immune categories among unique ancestry-specific variants 
```{r Enrichment of immune categories among unique ancestry-specific variants}
#Summarise
snps_anc_sum <-excl_snps2 %>%
  select(Global_response, general_ancestry, response, SNPS)%>%
  group_by(Global_response, general_ancestry, response, SNPS) %>%
  summarise(n_snp = n_distinct(SNPS), .groups = "drop") %>%
  unique()

snps_anc_sum <-snps_anc_sum %>%
  select(Global_response, general_ancestry, response) %>%
    count(Global_response, general_ancestry, response) 

# Plot  
fig3d <- ggplot(snps_anc_sum, aes(x = general_ancestry, y = response, color = Global_response)) +
  geom_point(aes(size = n )) +
  scale_size(range = c(1, 5)) +
  scale_color_manual(values = immune_response_pal)+ 
  theme_minimal() +
  labs(
    x = "Ancestry",
    y = "Immune Response Category",
    size = "Unique SNPs",
    color = "Proportion of unique SNPs",
    title = "D. Enrichment of immune categories among \n unique ancestry-specific variants"
  ) +
  theme(
    plot.title = element_text(size = 12, hjust = 0.5, face = "bold"),
    panel.grid.major.x = element_blank(),
    legend.position = "right",
    legend.box = "vertical",
    legend.title = element_blank(),
    axis.title.x = element_text(size = 8, face = "bold"),
    axis.title.y = element_text(size = 8, face = "bold"),
    axis.text.x = element_text(size =8))+
    guides(
    size = guide_legend(order = 1, hjust = 0.5),
    color = guide_legend(order = 2, hjust = 0.5))
fig3d

# Join plots
fig_3cd <- plot_grid(
  fig3c, fig3d,
  labels = c("", ""),
  ncol = 2,
  rel_heights = c(0.8,2)
)
fig_3cd

snps_anc_sum_perc <-  snps_anc_sum%>%
  group_by(general_ancestry, response) %>%
  summarise(total_response = sum(n)) %>%
  group_by(general_ancestry) %>%
  mutate(percentage = total_response / sum(total_response) * 100) %>%
  ungroup()

```

## STEP 9:  Figure 3e. Principal mapped genes associated to the ancestry-specific variants 
```{r Principal mapped genes associated to the ancestry-specific variants }
exc_genes <-immune_snps_2%>%
  select(general_ancestry, Global_response, SNPS, MAPPED_GENE)%>%
  count(general_ancestry, MAPPED_GENE) 

exc_genes <- exc_genes %>%
  filter(!is.na(MAPPED_GENE))

genes_exclusive <- exc_genes %>%
  group_by(MAPPED_GENE) %>%
  mutate(n_ancestries = n_distinct(general_ancestry)) %>%
  ungroup() %>%
  filter(n_ancestries == 1) %>%
  group_by(general_ancestry, MAPPED_GENE) %>%
  summarise(total_SNPs = sum(n), .groups = "drop") %>%
  arrange(general_ancestry, desc(total_SNPs))

# Choose the most frequent genes by ancestry
genes_exclusive_top <- genes_exclusive %>%
  group_by(general_ancestry) %>%
  slice_max(total_SNPs, n = 10, with_ties = FALSE)%>%
  ungroup()

# Plot
fig3e <- ggplot(genes_exclusive_top, 
       aes(x = reorder(MAPPED_GENE, total_SNPs), 
           y = total_SNPs, fill = general_ancestry)) +
  geom_col(show.legend = FALSE) +
  scale_fill_manual(values = ancestry_pal)+ 
  facet_wrap(~general_ancestry, scales = "free_y", ncol = 4) +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "E. Top mapped genes associated with ancestry-specific variants",
    x = "Mapped Gene",
    y = "Number of SNPs"
  ) +
  theme(
    plot.title = element_text(size = 12, hjust = 0.5,face = "bold"),
    panel.grid.major.x = element_blank(),
    strip.text = element_text(face = "bold"),
    legend.position = "right",
    legend.box = "vertical",
    legend.title = element_blank(),
    axis.title.x = element_text(size = 8, face = "bold"),
    axis.title.y = element_text(size = 8, face = "bold"),
    axis.text.x = element_text(size =8))

# Join plots for figure 3
fig_3 <- plot_grid(
  fig_3ab, fig_3cd, fig3e,
  labels = c("","",""),
  ncol = 1,
  rel_heights = c(1,1.5,1)
)
fig_3

ggsave(filename= "~/Documents/R/Review/Sept/Figures/Figure_3.pdf", plot= fig_3, width = 11, height = 15, dpi=300, units = "in", bg = "white" )

```